### 2018-04-06 reports/thesis/chapters/5_inference.tex
Organised the inference script, made script and section on empirical null filter, removed and changed some of ZTester methods.

>>>>

The empirical null filter was used on the example at the start of the chapter. It was used on a grid of $20\times 20$ points, the remaining values were interpolated. It was also assumed the empirical null standard deviation was constant, the methodology discussed in the previous paragraph.

\begin{figure}
	\centering
    \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/filter_z_image.eps}
        \caption{$z$ image}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/filter_p_image.eps}
        \caption{$\log p$-value image}
    \end{subfigure}
    }
    \caption{The $z$ image and $p$-value image after using the empirical null filter.}
    \label{fig:inference_filter_z_p_image}
\end{figure}

\begin{figure}
	\centering
    \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/filter_histogram.eps}
        \caption{Histogram of $z$ statistics}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/filter_p.eps}
        \caption{Ordered $p$ values}
    \end{subfigure}
    }
    \caption{Histogram of $z$ statistics and the corresponding ordered $p$-values}
    \label{fig:inference_filter_z_ordered_p}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=0.7\textwidth]{../figures/inference/filter_sig_image.eps}
	\caption{Using the empirical null filter, significant pixels were highlighted in red.} 
	\label{fig:inference_filter_sig_image}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=0.7\textwidth]{../figures/inference/filter_mean_null.eps}
	\caption{The estimated empirical null mean} 
	\label{fig:inference_filter_mean_null}
\end{figure}
